---
title: "Data Analysis Citro Hashed no CC no myeloid"
author: "Elijah Willie"
date: "March 19, 2019"
output: 
  html_document:
    keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load in required libraries
```{r}
setwd("/home/elijah/Documents/Clusterability")
rm(list = ls())
#library(sf)
library(Seurat)
library(fastcluster)
library(parallelDist)
library(tidyverse)
library(cluster)
library(Rclusterpp)
library(sigclust2)
library(data.table)
library(dendextend)
library(corrplot)
library(ape)
library(parallel)
library(agricolae)
library(lubridate)
library(factoextra)
library(clustertend)
library(Emcdf)
library("diptest")
library(Rtsne)
library(cluster)
library(survJamda)
#load helper functions
source("Helper_Functions.R")
#source("Consensus_Function.R")
source("SigClust_mod.R")
library(SingleCellExperiment)
library(scater)
library(SC3)
```


# Preprocess the data
```{r}
#create the seurat object
obj <- .CreateSeuratObj("Data/Citro_hash_noCycle_noMyeloid.txt", Pname = "Citro Hashed", minCells = 5, minGenes = 200, matrix = F, sep = "\t")

#VlnPlot(object = obj, features.plot = c("nGene", "nUMI"), nCol = 2)
#Preprocess the data
obj <- .PreProcess(obj, low_thres = c(200, -Inf, -Inf), high_thres = c(2500, 0.05, Inf))
obj <- ScaleData(obj, num.cores = 4)

#compute the number of variable genes
length(obj@var.genes)
```

# Sort the highly variable by dispersion
```{r}
#get the variable genes sorted
varGenes <- .SortGenes(obj)

#get the data containing the top genes
obj_sub <- .GetGeneData(obj, varGenes$gene)

#rm(obj)
#do some garbage collection
gc()
```

# Run the first test
```{r}
#create a sequence of numbers
seq_vals <- seq(50,350, by = 50)

#iterate over sequence values and run program
results <- NULL
for(val in seq_vals){
  result <- .run_dip(val, obj_sub, varGenes = varGenes)
  #plot the result
  plot(result$plot)
  results[[val/50]] = result
  gc()
}


#remove null values from the results
results <- Filter(Negate(is.null), results)
```
# Run significant clustering on top 350 Variable genes
```{r}
result <- .run_dip(350, obj_sub, varGenes = varGenes)
plot(result$plot, use_labs = "F") + ggtitle("Significance clustering on top 350 variable genes")
```



# Run the second test
```{r}
boot_pvals <- NULL
dist_list <- NULL
dip_results <- NULL
seq_vals <- seq(50,350, by = 50)
for(i in seq_vals){
  print(i)
  #permute the data
  permuted <- as.matrix(obj_sub[varGenes$gene[1:i], ])
    #.GetGeneData(obj,varGenes$gene[1:i])
    #GF_sub[sample(nrow(GF_sub), , replace=TRUE),]

  #compute the distance
  data_dist <- parallelDist(t(permuted))
  dist_list[[i/50]] <- data_dist
  gc()
  #compute the dip stat
  boot_pvals[[i/50]] <- dip.test(data_dist)$p.value
  #dip_results[[i/50]] <- dip(data_dist, full.result = T)
  gc()
}
boot_pvals
```

# Run the 3rd test
```{r}
#run consensus clustering
output <- .Boot_Con(t(obj_sub), obj, distance="euclidean", method="ward",nboot=100)

#extract the dendrogram
dend <- as.dendrogram(output$dendrogram)

#plot it
plot(dend, type = "rectangle", ylab = "Height", edgePar = list(col = 2:3, lwd = 2:1),main = "Consensus Tree",  leaflab = "none")

#compute the cluster assignments
assignments <- cutree(dend, 2)

#run the significance testing 
Sig_Res <- .sigclust(t(obj_sub), labels = assignments)

#print the p value
Sig_Res$p_norm
```
# compare the shc and the sigclust results

```{r}
shc_assignments <- cutree(result$shc$hc_dat, 2)
shc_sig_res <- sigclust2::sigclust(t(obj_sub), labels = shc_assignments)

# Create two dendrograms
dend1 <- dend
dend2 <- as.dendrogram (result$shc$hc_dat)

# Create a list to hold dendrograms
dend_list <- dendlist(dend1, dend2)

# Cophenetic correlation matrix
cor.dendlist(dend_list, method = "cophenetic")
```

# Perform PCA
```{r}
genes <- obj@data@Dimnames[[1]]
#first run PCA
obj <- RunPCA(object = obj, pc.genes = obj@var.genes, do.print = F, 
    genes.print = 5, pcs.compute = 25)


#extract the first PC
pc_1 <- as.matrix(GetCellEmbeddings(object = obj, reduction.type = "pca", dims.use = 1))

#compute the proportion variance explained
eigs <- obj@dr$pca@sdev^2
#compute the proportion variance explained
rbind(var = eigs, proportion = eigs/sum(eigs), Cumulative = cumsum(eigs)/sum(eigs))
```


# Perform pc significance testing
```{r}
#determine statistically significant PCs using jackstraw
obj <- JackStraw(object = obj, num.replicate = 100, display.progress = TRUE,  num.cores = 6,do.par = T)
obj <- JackStrawPlot(object = obj, PCs = 1:20, nCol = 5)

sig_indices <- which(obj@dr$pca@jackstraw@overall.p.values[, 2] < 0.05)
sig_pcs <- sum(obj@dr$pca@jackstraw@overall.p.values < 0.05)

# extract the significant PCs data
data_pca <- as.matrix(GetCellEmbeddings(object = obj, reduction.type = "pca", dims.use = sig_indices))
dirs <- obj@dr$pca@gene.loadings[, sig_indices]
#rm(obj)
gc()
# add consensus clustering metadata
#obj@meta.data$consensus.clusters <- assignments

# add significance clustering metadata
#n_sig <- sum(result$shc$nd_type == "sig")
#obj@meta.data$significance.clustering <- cutree(result$shc$hc_dat, n_sig+1)
# Run Tsne on the data
obj <- RunTSNE(object = obj, dims.use = 1:sig_pcs, do.fast = TRUE)

#plot tsne and color by significant cluster
#TSNEPlot(obj, group.by ="significance.clustering", title = "Nippo ALL Tsne")

#plot tsne and color by consensus clusters
#TSNEPlot(obj, group.by ="consensus.clusters", title = "Nippo ALL Tsne")

# run the dip test on the significant PCs
```


# Compute the density plots
```{r}
pdf("Results/Citro_Hash_No_CC_No_Myeloid_Density_Plots.pdf")

# on all the variable genes
varGenes_dist <- parallelDist(t(obj_sub))
varGenes_dip <- dip.test(varGenes_dist)$p.value
var_plot_vals <- melt(as.matrix(varGenes_dist))

hist(varGenes_dist, main = paste("Citro Hash density plot on all variable genes. \nDip Test p-value =", round(varGenes_dip, 4)), xlab = "Distance", probability = T, col = "lightblue")
lines(density(varGenes_dist), col="red", lwd=2)

gc()

# on just the significant PCs
pca_dist <- parallelDist(data_pca)
pca_dip <- dip.test(pca_dist)$p.value
pca_plot_vals <- melt(as.matrix(pca_dist))


hist(pca_dist, main = paste("Citro Hash density plot on significant PCs. \nDip Test p-value =", round(pca_dip,4)), xlab = "Distance", probability = T, col = "lightblue")
lines(density(pca_dist), col="red", lwd=2)

# on the first PC
pc_1_dip <- dip.test(pc_1)$p.value

hist(pc_1, main = paste("Citro Hash density plot on the first PC. \nDip Test p-value =", round(pc_1_dip,4)), xlab = "Distance", probability = T, col = "lightblue")
lines(density(pc_1), col="red", lwd=2)

dev.off()
```


# run the dip test on the significant PCs
```{r}
#perform the dip test on the pairwise distances between the significant PCs rotations
pca_dist <- parallelDist(data_pca)
dip_pca <- dip.test(parallelDist(data_pca))$p.value
```

```{r}
dist_full <- parallelDist(t(obj_sub[varGenes$gene[1:350], ]))
hist(dist_full, main = "Density Plot on top 350 variable genes", xlab = "Distance", probability = T, col = "red")
lines(density(dist_full), col="blue", lwd=2)
```

# Run dip test on the first two T-sne axes
```{r}
data_tsne <- as.matrix(GetCellEmbeddings(object = obj, reduction.type = "tsne", dims.use = 1:2))

#plot their histograms
hist(data_tsne[,1], main = "Density Plot of the first T-sne", col = "red", probability = T)
lines(density(data_tsne[,1]), col="blue", lwd=2)

hist(data_tsne[,2], main = "Density Plot of the second T-sne", col = "red", probability = T)
lines(density(data_tsne[,2]), col="blue", lwd=2)

# run the dip test
dip.test(data_tsne[,1])
dip.test(data_tsne[,2])
```

# Perform the dip test on the first principal component
```{r}
#lets get the density plot of the first pc
hist(pc_1, main = "Density Plot of the first PC", xlab = "Value", probability = T, col = "red")
lines(density(pc_1), col="blue", lwd=2)

#run the dip test
dip.test(pc_1)

```

# Save the plots
```{r}
pdf("Citro_no_CC_plots.pdf")

plot(result$plot, use_labs = F) + ggtitle("Significance clustering on top 350 variable genes")
plot(dend, type = "rectangle", ylab = "Height", edgePar = list(col = 2:3, lwd = 2:1),main = "Consensus Tree, p = 0.250",  leaflab = "none")

#plot the initial Tsne
TSNEPlot(obj) + ggtitle("Initial T-sne")

#plot tsne and color by significant cluster
TSNEPlot(obj, group.by ="significance.clustering") + ggtitle( "T-sne colored by significant nodes")

#plot tsne and color by consensus clusters
TSNEPlot(obj, group.by ="consensus.clusters") + ggtitle("T-sne colored by consensus nodes")

hist(dist_full, main = "Density Plot on top 350 variable genes", xlab = "Distance", probability = T, col = "red")
lines(density(dist_full), col="blue", lwd=2)

hist(pc_1, main = "Density Plot of the first PC", xlab = "Value", probability = T, col = "red")
lines(density(pc_1), col="blue", lwd=2)

dev.off()
```

# extract the significance and the consensus cluster labels
```{r}
all_labels <- dplyr::select(obj@meta.data, significance.clustering, consensus.clusters)
colnames(all_labels) <- c("Significance clustering", "Consensus clustering")

#write it to a csv file
write.csv(all_labels, file = "Citro_no_CC_plots.csv")
```

# principal curve analyses
```{r}
fit <- principal_curve(data_pca, trace = T, plot_iterations = T)
```

#plot a histogram of the projections
```{r}
#fit_dist <- parallelDist(fit$s[])
fit_dip <- dip.test(fit$s[, 1])$p.value
hist(fit$lambda, breaks = 100, main = paste("Citro Hash No CC No Myeloid density plot on Principal Curves. \nDip Test p-value =", round(fit_dip, 4)), xlab = "Distance", probability = T, col = "lightblue")
lines(density(fit$lambda), col="red", lwd=2)
```

# Perform PCA
```{r}
sig_pcs_list <- NULL
data_pca_list <- NULL
dip_list <- NULL
seq_vals <- seq(50,700, by = 50)
pdf("Results/Citro_Hash_No_CC_No_Myeloid_All_Density_Z_Score_plots.pdf")
for(i in seq_vals){
  #first run PCA
obj <- RunPCA(object = obj, pc.genes = varGenes$gene[1:i], do.print = F, pcs.print = 1:5, 
    genes.print = 5, pcs.compute = 25)

#compute the proportion variance explained
eigs <- obj@dr$pca@sdev^2
#compute the proportion variance explained
rbind(var = eigs, proportion = eigs/sum(eigs), Cumulative = cumsum(eigs)/sum(eigs))

#extract the first PC
#pc_1 <- as.matrix(GetCellEmbeddings(object = obj, reduction.type = "pca", dims.use = 1))


# Perform pc significance testing
gc()
#determine statistically significant PCs using jackstraw
obj <- JackStraw(object = obj, num.replicate = 100, num.cores = 4,do.par = T, display.progress = F)
obj <- JackStrawPlot(object = obj, PCs = 1:20, nCol = 5)

sig_indices <- which(obj@dr$pca@jackstraw@overall.p.values[, 2] < 0.05)

sig_pcs <- sum(obj@dr$pca@jackstraw@overall.p.values < 0.05)
sig_pcs_list[[i/50]] <- sig_pcs

# extract the significant PCs data
data_pca <- as.matrix(GetCellEmbeddings(object = obj, reduction.type = "pca", dims.use = sig_indices))
pca_dist <- znorm(parallelDist(data_pca))
data_pca_list[[i/50]] <- pca_dist

# run the dip test
pca_dip <- dip.test(pca_dist)$p.value
dip_list[[i/50]] <- pca_dip

hist(pca_dist, breaks = 300, main = paste("Citro Hash density plot on significant PCs on", i, "variable genes", "\nDip Test p-value =", round(pca_dip,4)), xlab = "Distance", probability = T, col = "lightblue")
lines(density(pca_dist), col="red", lwd=2)


  
}
dev.off()
```


# plot some results
```{r}

plot_vals <- data.frame("NumGenes" = seq_vals, "DipTest" = dip_list, "NumSigPcs" = sig_pcs_list)

par(mfrow=c(2,2))
plot(plot_vals$NumGenes, -log10(plot_vals$DipTest), xlab = "Number of variable genes", ylab = "log10(Dip test p-value)", main = "Dip test as a function of variable genes \n Red points (p < 0.05)",  col=ifelse(plot_vals$DipTest < 0.05,"red","black"), ylim = c(0, 5))

plot(plot_vals$NumGenes, plot_vals$NumSigPcs, xlab = "Number of variable genes", ylab = "Number of significant PCs", main = " Num  Sig PCs as a function of variable genes")

plot(plot_vals$NumSigPcs, -log10(plot_vals$DipTest), xlab = "Number of Significant PCs", ylab = "log10(Dip test p-value)", main = "Dip test as a function of Sig PCs \n Red points (p < 0.05)",  col=ifelse(plot_vals$DipTest < 0.05,"red","black"), ylim = c(0, 5))

```

# Auto encoders
```{r}
# set training data
x_train <- as.matrix(t(obj_sub))

# set model
model <- keras_model_sequential()
model %>%
  layer_dense(units = 6, activation = "tanh", input_shape = ncol(x_train)) %>%
  layer_dense(units = 2, activation = "tanh", name = "bottleneck") %>%
  layer_dense(units = 6, activation = "tanh") %>%
  layer_dense(units = ncol(x_train))

# view model layers
summary(model)

# compile model
model %>% compile(
  loss = "mean_squared_error", 
  optimizer = "adam"
)

# fit model
model %>% fit(
  x = x_train, 
  y = x_train, 
  epochs = 2000,
  verbose = 0
)

# evaluate the performance of the model
mse.ae2 <- evaluate(model, x_train, x_train)
mse.ae2

# extract the bottleneck layer
intermediate_layer_model <- keras_model(inputs = model$input, outputs = get_layer(model, "bottleneck")$output)
intermediate_output <- predict(intermediate_layer_model, x_train)
```

#plot it
```{r}
ggplot(data.frame(Dim1 = intermediate_output[,1], Dim2 = intermediate_output[,2]), aes(x = Dim1, y = Dim2)) + geom_point()
```

# run dip test
```{r}
encoder_dist <- parallelDist(intermediate_output)
plot(density(encoder_dist))
dip.test(encoder_dist)
```

# PPCI
```{r}
X <- t(obj_sub)

# perform Maximum Clusterability Dimension Reduction
sol <- mcdr(X, 10)

# plot results and run dip test
sol_dist <- parallelDist(sol$fitted)
plot(density(sol_dist))
dip.test(sol_dist)
```


# Maximum Clusteriability Hyperplane
```{r}
X <- t(obj_sub)
sol <- mch(X)
plot(sol)
plot(sol$fitted[, 1], sol$fitted[, 2])
sol_dist <- parallelDist(sol$fitted, method = "minkowski", p = 2)
plot(density(sol_dist))
dip.test(sol_dist)
```

# Minimum Density Hyperplane
```{r}
X <- t(obj_sub)
sol <- mdh(X)
#pdf("Results/Citro_no_CC_Hyperplane_Sig_PCs_plots.pdf")
plot(sol)
sol_dist <- parallelDist(sol$fitted)
dip_stat <- dip.test(sol_dist)$p.value

plot(sol$fitted[, 1], sol$fitted[, 2], xlab = "Plane 1", ylab = "Plane 2", main = "Minimum density hyperplane data projection")
hist(sol_dist, breaks = 100, main = paste("Citro no CC Sig Pcs density plot on Min Density Hyperplane", "\nDip Test p-value =", round(dip_stat,4)), xlab = "Distance", probability = T, col = "lightblue")
lines(density(sol_dist), col="red", lwd=2)

#dev.off()
```

# Minimum Density Hyperplane on varying number of variable genes
```{r}
dip_list <- NULL
seq_vals <- seq(50,700, by = 50)
pdf("Results/Citro_NoCC_Min_Density_hyperplane_Sig_PCs_plots.pdf")
for(i in seq_vals){

  obj <- RunPCA(object = obj, pc.genes = varGenes$gene[1:i], do.print = F, pcs.print = 1:5, 
    genes.print = 5, pcs.compute = 25)
  
  gc()
  
  #determine statistically significant PCs using jackstraw
  obj <- JackStraw(object = obj, num.replicate = 100, num.cores = 4,do.par = T, display.progress = F)
  obj <- JackStrawPlot(object = obj, PCs = 1:20, nCol = 5)
  sig_indices <- which(obj@dr$pca@jackstraw@overall.p.values[, 2] < 0.05)
  
  # extract the variable genes data
  X <- t(.GetGeneData(obj, varGenes$gene[1:i]))
  dirs <- obj@dr$pca@gene.loadings[, sig_indices]
  
  # get the minimum density hyper planes
  sol <- mdh(X,v0 = dirs)
  
# run the dip test
sol_dist <- parallelDist(sol$fitted)
dip_stat <- dip.test(sol_dist)$p.value
dip_list[i/50] <- dip_stat

hist(sol_dist, breaks = 300, main = paste("Citro No CC density plot on significant PCs on", i, "variable genes", "\nDip Test p-value =", round(dip_stat,4)), xlab = "Distance", probability = T, col = "lightblue")
lines(density(sol_dist), col="red", lwd=2)
  
}
dev.off()
```


# SCRNA GLM PCA

```{r}
# source the required packages
source("/home/elijah/Documents/scrna2019/algs/glmpca.R")
source("/home/elijah/Documents/scrna2019/util/functions.R")
source("/home/elijah/Documents/scrna2019/util/functions_genefilter.R")

# get counts
counts <- fread("Data/Citro_hash_noCycle_noMyeloid.txt") %>% column_to_rownames(var = "V1")

# run SCRNA
 res <- .RunScrna(counts_data = counts, dim = 2, nGenes = 1000)
  
  # compute the correlation between the residuals
  res_cor <- (1 - WGCNA::cor(res$residuals))/2
  res_cor_dip <- dip.test(res_cor)$p.value
  plot(density(res_cor), xlab = "Correlation", ylab = "Density", main = paste("Residual-Correlation Dip pval = ", round(res_cor_dip, 4)))
  
  # compute the euclidean distances between the residuals
  res_eucl <- parallelDist(t(res$residuals))
  res_eucl_dip <- dip.test(res_eucl)$p.value
  plot(density(res_eucl), xlab = "Distance", ylab = "Density", main = paste("Residual-Euclidean Dip pval = ", round(res_eucl_dip, 4)))
  
  # run the dip test on the results
  plot(res$pca_residuals$x[, 1:2], main = "SCRNA PCA Plot")
  glm_dist <- parallelDist(as.matrix(res$pca_residuals$x[,1:2]))
  glm_dip <- dip.test(glm_dist)$p.value
  plot(density(glm_dist), xlab = "Distance", ylab = "Density", main = paste("GLM-PCA Dip pval = ", round(glm_dip, 4)))

  glm_corr <- (1 - WGCNA::cor(t(res$pca_residuals$x)))
  glm_corr_dip <- dip.test(glm_corr)$p.value
  
  # run MDH on the residuals
  glm_mdh <- mdh(t(res$residuals), v0 = res$pca_residuals$rotation[, 1])
  plot(glm_mdh)
  glm_mdh_dist <- parallelDist(glm_mdh$fitted)
  glm_mdh_dip <- dip.test(glm_mdh_dist)$p.value
  plot(density(glm_mdh_dist), xlab = "Distance", ylab = "Density", main = paste("Residual-MDH Dip pval = ", round(glm_mdh_dip, 4)))
```

# Run SWNE
```{r}
library(swne)
# run swne
swne.emb <- swne::RunSWNE(obj_sub, proj.method = "umap", dist.metric = "correlation", n.cores = 4)

# plot the results
plot(swne.emb$sample.coords)

# run dip test and plot the results
swne.dist <- parallelDist(as.matrix(swne.emb$sample.coords))
swne.dip <- dip.test(swne.dist)$p.value
plot(density(swne.dist), main = paste("Dip Pval = ", round(swne.dip, 4)))
```

# Principal Curve on SCRNA
```{r}
counts <- fread("Data/Citro_hash_noCycle_noMyeloid.txt") %>% column_to_rownames(var = "V1")
resids <- .RunScrna(counts_data = counts, dim = 2, nGenes = 500)$residuals
pc <- pcurve(x = t(resids), start = "pca", penalty = 2, cv.fit = T, cv.all = T, plot.init = F, plot.resp = F, plot.segs = T, fit.meth = "lowess")
```

# Splatter simulation based on data
```{r}
params <- splatEstimate(as.matrix(counts))

sce <- sce <- splatSimulate(params = params, batchCells = 500,
                     group.prob = c(0.13, 0.07, 0.1, 0.05, 0.4, 0.1, 0.1, 0.05), 
                     method = "groups", 
                     de.prob = c(0.03, 0.03, 0.03, 0.05, 0.05, 0.07, 0.08, 0.1),
                     verbose = FALSE)
```

# Run SCRNA on simulation
```{r}
counts <- counts(sce)

# run SCRNA
 res <- .RunScrna(counts_data = counts, dim = 2, nGenes = 1000)
  
  # compute the correlation between the residuals
  res_cor <- (1 - WGCNA::cor(res$residuals))/2
  res_cor_dip <- dip.test(res_cor)$p.value
  plot(density(res_cor), xlab = "Correlation", ylab = "Density", main = paste("Residual-Correlation Dip pval = ", round(res_cor_dip, 4)))
  
  # compute the euclidean distances between the residuals
  res_eucl <- parallelDist(t(res$residuals))
  res_eucl_dip <- dip.test(res_eucl)$p.value
  plot(density(res_eucl), xlab = "Distance", ylab = "Density", main = paste("Residual-Euclidean Dip pval = ", round(res_eucl_dip, 4)))
  
  # run the dip test on the results
  plot(res$pca_residuals$x[, 1:2], main = "SCRNA PCA Plot")
  glm_dist <- parallelDist(as.matrix(res$pca_residuals$x[,1:2]))
  glm_dip <- dip.test(glm_dist)$p.value
  plot(density(glm_dist), xlab = "Distance", ylab = "Density", main = paste("GLM-PCA Dip pval = ", round(glm_dip, 4)))

  glm_corr <- (1 - WGCNA::cor(t(res$pca_residuals$x)))
  glm_corr_dip <- dip.test(glm_corr)$p.value
  
  # run MDH on the residuals
  glm_mdh <- mdh(t(res$residuals), v0 = res$pca_residuals$rotation[, 1])
  plot(glm_mdh)
  glm_mdh_dist <- parallelDist(glm_mdh$fitted)
  glm_mdh_dip <- dip.test(glm_mdh_dist)$p.value
  plot(density(glm_mdh_dist), xlab = "Distance", ylab = "Density", main = paste("Residual-MDH Dip pval = ", round(glm_mdh_dip, 4)))

```
