---
title: "DE_Analysis"
author: "Elijah Willie"
date: "December 28, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

# Load Required libraries and files

```{r}
setwd("/home/elijah/Documents/Clusterability")
rm(list = ls())
library(Seurat)
library(fastcluster)
library(parallelDist)
library(tidyverse)
library(cluster)
library(Rclusterpp)
library(sigclust2)
library(data.table)
library(dendextend)
library(corrplot)
library(ape)
library(parallel)
library(agricolae)
library(lubridate)
library(factoextra)
library(clustertend)
library(Emcdf)
library("diptest")
library("silvermantest")
library(Rtsne)
#load helper functions
source("Helper_Functions.R")
#source("Consensus_Function.R")
```

## Preprocess the data
```{r}
#create the seurat object
obj <- .CreateSeuratObj("Data/Polygrus_hashed.txt", Pname = "SAL", minCells = 5, minGenes = 200, matrix = F, sep = "\t")

#Preprocess the data
obj <- .PreProcess(obj, low_thres = c(200, -Inf), high_thres = c(2500, 0.05))
```

## Run the pipeline
```{r}
#create a sequence of numbers
seq_vals <- seq(50,500, by = 50)

#iterate over sequence values and run program
results <- NULL
for(val in seq_vals){
  result <- .RunPipeline(Ngenes = val, obj, De_plot = F)
  results[[val/50]] = result
}


#remove null values from the results
results <- Filter(Negate(is.null), results)
```

## Evaluate the results

To evaluate the results, I am curious about the following
* How many genes are conserved as we move down in the significance tree
* How many genes are conserved as we increase the pool size 

```{r}
#get the list of all the DE genes across all gene sets
union_list <- as.data.frame(unlist(ComputeSet(results)))
colnames(union_list) <- c("genes")

#get the list of conserved DE genes for each significant node
# intersect_list <- as.data.frame(unlist(ComputeSet(results, type = "intersect")))
# intersect_list <- as.data.frame(intersect_list[complete.cases(intersect_list), ])

#create a table showing how ofen each gene was found significant
freq_table <- table(union_list)

#sort the table
freq_table <- as.data.frame(sort(freq_table, decreasing = T))
colnames(freq_table) <- c("gene", "Frequency")

#get the list of conserved genes across all genesets
# conserved_genes <- unique(intersect_list)
# colnames(conserved_genes) <- c("genes")


```

## Compute some tree distances

```{r}
d1 <- as.dendrogram(results[[1]]$sigclust$hc_dat)

d2 <- as.dendrogram(results[[2]]$sigclust$hc_dat)

d3 <- as.dendrogram(results[[3]]$sigclust$hc_dat)

d4 <- as.dendrogram(results[[4]]$sigclust$hc_dat)

# d5 <- as.dendrogram(results[[5]]$sigclust$hc_dat)
# 
# d6 <- as.dendrogram(results[[6]]$sigclust$hc_dat)
# 
# d7 <- as.dendrogram(results[[7]]$sigclust$hc_dat)
# 
# d8 <- as.dendrogram(results[[8]]$sigclust$hc_dat)
# 
# d9 <- as.dendrogram(results[[9]]$sigclust$hc_dat)

#d10 <- as.dendrogram(results[[10]]$sigclust$hc_dat)
gc()

# 
dends <- dendlist(d1, d2, d3, d4)

result_diffs <- all.equal(dends)
corr_vals <- cor.dendlist(dends)

corrplot.mixed(corr_vals, title = "GF Top N Var Genes", mar=c(0,0,1,0))
```
```{r}
trees <- NULL
for(i in 1:length(results)){
  trees[[i]] <- as.phylo(results[[1]]$sigclust$hc_dat)
}
```


```{r}
con_tree <- consensus.edges(trees)
```

#run consensus clustering
```{r}
#create a sequence of numbers
# seq_vals <- seq(50,500, by = 50)
dends <- NULL
DD <- matrix(0, nrow(temp), nrow(temp))

for(i in seq(1,20,1)){
  print(i)
  perm_dat <- temp[, sample(ncol(temp), 100, replace = F)]
  
  dist_mat <- parallelDist(perm_dat, method = "euclidean")
  
  #run the clustering algorithm
  dend <- fastcluster::hclust(dist_mat, method = "ward.D2")
  #compute the dendrogram
  # dend <- .GenerateConsensus(val, obj)
  
  #cut the tree to get two clusters and get the labels
  assignments <- cutree(dend, 2)
  
  #check if observations are in the same cluster or not
  dd<-as.matrix(dist(assignments))
  #set distance to 1 if not in same cluster
  dd[dd!=0]<-1
  # dd all distances together across 50 iterations
  DD<-DD+(1-dd) 
  
}

#cluster based on consensus
hc <- hclust(as.dist(1-DD/length(seq_vals)), method = "ward.D2")

hc <- as.dendrogram(hc)

#plot the resulting dendrogram
plot(hc,  ylab = "Height", edgePar = list(col = 2:3, lwd = 2:1), main = "SPF Consensus Dendrogram")


```

# Save the plots from the significant clustering

```{r}
#save the plots in a pdf documnent
PDF_Path <- "/home/elijah/Documents/Clusterability/BR_Sig_Plots.pdf"
pdf(file=PDF_Path)

for(i in 1:length(results)){
  plot(results[[i]]$plot)
}
dev.off() 
```

# Run significant clustering using bootstrapping

## Do some preprocessing first
```{r}
#get the variable genes sorted
varGenes <- .SortGenes(obj)

#get the top 500 Genes
#top_N <- varGenes$gene[1:500]

#get the data containing the top 500
obj_sub <- .GetGeneData(obj, varGenes$gene[1:500])

```

## Run the bootstrapping
```{r}
system.time(boot_clusters <- .BootClust(n_iter = 100, n_genes = 100, dat = obj_sub))

```


## Compute the ultrametric distances for all the trees
```{r}
system.time(U_list <- lapply(boot_clusters, cl_ultrametric))
```

## Average over all matrices

```{r}
U_avg <- Reduce("+", U_list) / length(U_list)
```


## Compute and plot the resulting consensus dendrogram

```{r}
output <- .Boot_Con(t(obj_sub), obj, distance="euclidean", method="ward",nboot=100)

dend <- as.dendrogram(output$dendrogram)

plot(dend, type = "rectangle", ylab = "Height", edgePar = list(col = 2:3, lwd = 2:1))

assignments <- cutree(dend, 2)

```


# Save the plots from the significant clustering

```{r}
Sig_Res <- sigclust(t(obj_sub), labels = assignments)
```

## Read in and preprocess all the datasets
```{r}
#read in the datas
GF <- .CreateSeuratObj("matrix_GF_naive.txt", Pname = "GF", minCells = 5, minGenes = 200, matrix = F)
Citro <- .CreateSeuratObj("matrix_citrobacter_Tconvs.txt", Pname = "Citro", minCells = 5, minGenes = 200, matrix = F)
BR <- .CreateSeuratObj("matrix_GF_naive.txt", Pname = "BR", minCells = 5, minGenes = 200, matrix = T)


#Preprocess the data
GF <- .PreProcess(GF, low_thres = c(200, -Inf), high_thres = c(2500, 0.05))
Citro <- .PreProcess(Citro, low_thres = c(200, -Inf), high_thres = c(2500, 0.05))
BR <- .PreProcess(BR, low_thres = c(200, -Inf), high_thres = c(2500, 0.05))

#get the variable genesdata
GF_VarGenes <- .SortGenes(GF)
GF_sub <- .GetGeneData(GF, GF_VarGenes$gene)
Citro_VarGenes <- .SortGenes(Citro)
Citro_sub <- .GetGeneData(Citro, Citro_VarGenes$gene)
BR_VarGenes <- .SortGenes(BR)
BR_sub <- .GetGeneData(BR, BR_VarGenes$gene)
```

## Run the tests on all the datasets
```{r}
GF_results <- .RunTests(GF_sub)
Citro_results <- .RunTests(Citro_sub)
BR_results <- .RunTests(BR_sub)
```



## Generate the results
```{r}
result <- data.frame(matrix(,3,2))

#rename the rows and columns
colnames(result) <- c("Dip Dist", "PCA Dip")
rownames(result) <- c("GF", "Citro", "BR")

#populate the results table
result[1, ] <- unlist(GF_results)
result[2, ] <- unlist(Citro_results)
result[3, ] <- unlist(BR_results)

```



# Peform some seurat analyses and run the dip test
```{r}
genes <- obj@data@Dimnames[[1]]
#first run PCA
obj <- RunPCA(object = obj, pc.genes = obj@var.genes, do.print = TRUE, pcs.print = 1:5, 
    genes.print = 5)

#determine statistically significant PCs using jackstraw
obj <- JackStraw(object = obj, num.replicate = 100, display.progress = TRUE)
JackStrawPlot(object = obj, PCs = 1:15)

#seems only the first 3 PCs are significant
data_pca <- as.matrix(GetCellEmbeddings(object = obj, reduction.type = "pca", dims.use = 1:3))

#perform the dip test on the significant PCs rotations
dip_pca <- dip.test(data_pca)$p.value

# Run Tsne on the data
obj <- RunTSNE(object = obj, dims.use = 1:3, do.fast = TRUE)
TSNEPlot(obj)

#get the tsne data
data_tsne <- GetCellEmbeddings(object = obj, reduction.type = "tsne", dims.use = 1:2)

#run the dip test on the tsne data
dip_tsne <- dip.test(data_tsne)$p.value
```


# Lets run traditional Tsne
```{r}
#extract the highly variable genes data
obj_var <- t(.GetGeneData(obj, obj@var.genes))

#run Tsne
tsne <- Rtsne(obj_var, dims = 9, perplexity=30, verbose=TRUE, max_iter = 500, num_threads = 0, pca = F)

plot(tsne$Y)
#run the dip test on the results
rtsne_dip <- dip(tsne$Y)
```

# Run tests as we vary the gene sizes
```{r}
#create a sequence of numbers
seq_vals <- seq(50,500, by = 50)

plots <- NULL
#iterate over sequence values and run program
#dip_vals_GF <- NULL
#dip_vals_Citro <- NULL
#dip_vals_BR <- NULL
PDF_Path <- "/home/elijah/Documents/Clusterability/BR_Dist_Histograms.pdf"
pdf(file=PDF_Path)
for(val in seq_vals){
  
  #select the top n genes for each dataset
  #For GF
  #data_GF <-.GetGeneData(GF,GF_VarGenes$gene[1:val])
  #GF_dist <- as.matrix(parallelDist(t(data_GF)))

  #for Citro
  #data_Citro <-.GetGeneData(Citro,Citro_VarGenes$gene[1:val])
  #Citro_dist <- as.matrix(parallelDist(t(data_Citro)))
  
  
  #for BR
  data_BR <-.GetGeneData(BR,BR_VarGenes$gene[1:val])
  BR_dist <- as.matrix(parallelDist(t(data_BR)))
  hist(BR_dist, xlab = "Pairwise Distance", main = paste("Histogram of pairwise distances on", val, "Genes"))
  #plots[[val/50]] <- p
  
  #gc()
  #run the dip test
  #dip_vals_GF[[val/50]] <- dip.test(t(GF_dist))$p.value
  #dip_vals_Citro[[val/50]] <- dip.test(t(Citro_dist))$p.value
  #dip_vals_BR[[val/50]] <- dip.test(t(BR_dist))$p.value
  #gc()
  
}

dev.off() 
```


```{r}
boot_pvals <- NULL
dist_list <- NULL
dip_results <- NULL
seq_vals <- seq(50,500, by = 50)
for(i in seq_vals){
  print(i)
  #permute the data
  permuted <- .GetGeneData(obj,varGenes$gene[1:i])
    #GF_sub[sample(nrow(GF_sub), , replace=TRUE),]

  #compute the distance
  data_dist <- parallelDist(t(permuted))
  dist_list[[i/50]] <- data_dist
  #compute the dip stat
  boot_pvals[[i/50]] <- dip.test(data_dist)$p.value
  dip_results[[i/50]] <- dip(data_dist, full.result = T)
  gc()
}
```


# Put the results into a table
```{r}
results_500 <- data.frame(matrix(,3,10))
rownames(results_500) <- c("GF", "Citro", "BR")
colnames(results_500) <- c("50", "100", "150", "200", "250", "300", "350", "400", "450", "500")

results_500[1, ] <- dip_vals_GF
results_500[2, ] <- dip_vals_Citro
results_500[3, ] <- dip_vals_BR

#write it to csv
write.csv(results_500, file = "Top_Genes_Dip_Values.csv", sep = ",")
```


# Run dip test on the first 10 nodes of the datasets
```{r}
#perform clustering
BR_dist <- parallelDist(t(BR_sub))
n <- nrow(t(BR_sub))
BR_clusters <- hclust(BR_dist, method = "ward.D2")

idx <- .idx_hc(BR_clusters, n)
#run dip test on top 10 nodes
for(i in 1:10){
  full_dat <- rbind(t(BR_sub)[idx[[i]], ], t(BR_sub)[idx[[i+n-1]],])
  print(dip.test(parallelDist(as.matrix(full_dat)))$p.value)
  gc()
}
```


# Run dip test on shc significant nodes
```{r}
#create a sequence of numbers
seq_vals <- seq(50,500, by = 50)

#iterate over sequence values and run program
results <- NULL
for(val in seq_vals){
  result <- .run_dip(val, obj)
  results[[val/50]] = result
  gc()
}


#remove null values from the results
results <- Filter(Negate(is.null), results)
```

#plot the ecdf
```{r}
for(i in length(dist_list)){
  #compute the ecdf
  t1 <- ecdf(dist_list[[i]])
  
  gc()
  
  #plot the ecdf
  plot(t1, xlab = "Pairwise Distances", main = paste("Ecdf for BR on", i*50, "genes"))
  
  gc()
}
```


```{r}
temp <- dip(t(obj_sub), full.result = T)
```

