---
title: "Simulations"
author: "Elijah Willie"
date: "15/07/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load required librares
```{r}
rm(list = ls())
gc()
suppressPackageStartupMessages({
  library(Seurat)
  library(fastcluster)
  library(parallelDist)
  library(tidyverse)
  library(cluster)
  library(data.table)
  library("diptest")
  library(Rtsne)
  library(PPCI)
  library(splatter)
  library(SC3)
  library(scater)
  library(SingleCellExperiment)
  library(jackstraw)
  library(irlba)
  library(WGCNA)
  library(Rfast)
  library(gridExtra)
  library(reticulate)
  library(corpcor)
  library(cowplot)
  library(umap)
  library(Rtsne)
  library(sctransform)
  library(pheatmap)
  library(ggplotify)
  library(mvcluster)
}
)
setwd("/home/elijah/Documents/Clusterability")
source("Helper_Functions.R")
source("/home/elijah/Documents/scrna2019/algs/glmpca.R")
source("/home/elijah/Documents/scrna2019/util/functions.R")
source("/home/elijah/Documents/scrna2019/util/functions_genefilter.R")
source("Pipeline_Functions.R")
```

# Simulate increasing dimensionality with a single cluster
```{r}
# lists to hold test proportions
# Seurat
seurat_raw_props <- c()
seurat_pc_props <- c()
seurat_mdh_props <- c()

# Scrna
scrna_raw_props <- c()
scrna_pc_props <- c()
scrna_mdh_props <- c()

# SC3
sc3_k <- c()

# simulation parameters
# prob_vec <- c(1/3, 1/3, 1/3)
genes_dim <- seq(1500, 15000, 500)

for(i in genes_dim){
  
  cat(paste("\nRunning on",i,"Genes\n"))
  
  params.groups <- newSplatParams(batchCells = 2000, nGenes = i, seed = 1994)
  
  # run simulations
  sim <- splatSimulateGroups(params.groups, verbose = FALSE)
  
  # sim_norm <- scater::normalize(sim)
  # p <- plotPCA(sim_norm, colour_by = "Group")
  # plot(p)
  
  # extract the counts
  sim_counts <- counts(sim)
  
  # run the pipeline
  obj <- CreateModalityObject(sim_counts)
  
  # add the seurat slot
  obj <- PreprocessObject(obj,  nFeatures = 1000)
  
  # add the scrna slot
  obj <- PreprocessObject(obj, method = "Scrna", nFeatures = 1000)
  
  # Run the Seurat modality tests
  obj <- TestModality(obj)
  obj <- TestModality(obj, type = "Scrna")
  
  # compute a result table for all the tests
  seurat <- as.data.frame(unlist(obj@Tests$Seurat))
  colnames(seurat) <- c("Seurat.Dip.Pvalue")
  
  scrna <- as.data.frame(unlist(obj@Tests$Scrna))
  colnames(scrna) <- c("Scrna.Dip.Pvalue")
  
  res_table <- cbind(scrna, seurat)
  
  # compute the proportions of passed test
  obj <- ComputeProportions(obj)
  
  # update the proportions
  # Seurat
  seurat_raw_props <- c(seurat_raw_props, obj@Tests$Seurat$Proportions$seurat_raw)
  seurat_pc_props <- c(seurat_pc_props, obj@Tests$Seurat$Proportions$seurat_pc)
  seurat_mdh_props <- c(seurat_mdh_props, obj@Tests$Seurat$Proportions$seurat_mdh)
  
  # Scrna
  scrna_raw_props <- c(scrna_raw_props, obj@Tests$Scrna$Proportions$scrna_raw)
  scrna_pc_props <- c(scrna_pc_props, obj@Tests$Scrna$Proportions$scrna_pc)
  scrna_mdh_props <- c(scrna_mdh_props, obj@Tests$Scrna$Proportions$scrna_mdh)
  
  rm(obj)
  gc()
  
}

Seurat_props <- data.frame(genes_dim, seurat_raw_props, seurat_pc_props, seurat_mdh_props)
colnames(Seurat_props) <- c("nGenes", "Baseline", "PCA", "MDH")

Seurat_melted <- data.table::melt(Seurat_props, id.vars = "nGenes", variable.name = "Reduction")

p1 <- ggplot2::ggplot(Seurat_melted) + geom_point(aes(nGenes, value, color = Reduction)) +
                                        xlab("Number of Genes") + ylab("Proportion") + theme_gray() +
                                            ggtitle("Seurat Significance Proportions") +
                                                  facet_grid(. ~ Reduction) 

Scrna_props <- data.frame(genes_dim, scrna_raw_props, scrna_pc_props, scrna_mdh_props)
colnames(Scrna_props) <- c("nGenes", "Baseline", "PCA", "MDH")

Scrna_melted <- data.table::melt(Scrna_props, id.vars = "nGenes", variable.name = "Reduction")

p2 <- ggplot2::ggplot(Scrna_melted) + geom_point(aes(nGenes, value, color = Reduction)) +
                                        xlab("Number of Genes") + ylab("Proportion") + theme_gray() +
                                            ggtitle("Scrna significance proportions") +
                                                  facet_grid(. ~ Reduction) 
  
```

## save the plots
```{r}
pdf("/home/elijah/Documents/Clusterability/Results/Pipeline/Simulations/Genes_Proportions_Plots_1000.pdf", width = 12, height = 8)
t1 <- arrangeGrob(p1, p2, ncol = 2)
plot(t1)
dev.off()
```
## write files to csv
```{r}
write.csv(Seurat_props, 
          file = "/home/elijah/Documents/Clusterability/Results/Pipeline/Simulations/Seurat_Genes_Proportions_Plots_1000.csv")

write.csv(Scrna_props, 
          file = "/home/elijah/Documents/Clusterability/Results/Pipeline/Simulations/Scrna_Genes_Proportions_Plots_1000.csv")
```


# Simulate increasing cluster overlap
```{r}
overlap_seq <- seq(0, 0.5, 0.005)

# lists to hold test proportions
# Seurat
seurat_raw_props <- c()
seurat_pc_props <- c()
seurat_mdh_props <- c()

# Scrna
scrna_raw_props <- c()
scrna_pc_props <- c()
scrna_mdh_props <- c()

# simulation parameters
prob_vec <- c(1/3, 1/3, 1/3)

for(i in overlap_seq){
  
  cat(paste("\nRunning on",i,"Overlap\n"))
  
  params.groups <- newSplatParams(batchCells = 3000, nGenes = 2000, seed = 1994)
  
  # run simulations
  sim <- splatSimulateGroups(params.groups, group.prob = prob_vec, de.facLoc = c(1,1,1)*i,
                               de.facScale = c(1,1,1)*i, verbose = FALSE)
  
  sim_norm <- scater::normalize(sim)
  p4 <- plotPCA(sim_norm, colour_by = "Group") + ggtitle(paste("PCA plot of 3 groups with cluster overlap of 0.3"))
  # 
  
  # extract the counts
  sim_counts <- counts(sim)
  
  # run the pipeline
  obj <- CreateModalityObject(sim_counts)
  
  # add the seurat slot
  obj <- PreprocessObject(obj,  nFeatures = 1000)
  
  # add the scrna slot
  obj <- PreprocessObject(obj, method = "Scrna", nFeatures = 1000)
  
  # Run the Seurat modality tests
  obj <- TestModality(obj)
  obj <- TestModality(obj, type = "Scrna")
  
  # sc3 analysis
  # sc3_sce <- SingleCellExperiment(
  #     assays = list(counts = obj@Data$cleaned)
  # )
  # sc3_sce <- normalize(sc3_sce)
  # 
  # sc3_sce <- sc3_estimate_k(sc3_sce)
  # sc3_sce@metadata$sc3
  # 
  
  # compute a result table for all the tests
  seurat <- as.data.frame(unlist(obj@Tests$Seurat))
  colnames(seurat) <- c("Seurat.Dip.Pvalue")
  
  scrna <- as.data.frame(unlist(obj@Tests$Scrna))
  colnames(scrna) <- c("Scrna.Dip.Pvalue")
  
  res_table <- cbind(scrna, seurat)
  
  # compute the proportions of passed test
  obj <- ComputeProportions(obj)
  
  # update the proportions
  # Seurat
  seurat_raw_props <- c(seurat_raw_props, obj@Tests$Seurat$Proportions$seurat_raw)
  seurat_pc_props <- c(seurat_pc_props, obj@Tests$Seurat$Proportions$seurat_pc)
  seurat_mdh_props <- c(seurat_mdh_props, obj@Tests$Seurat$Proportions$seurat_mdh)
  
  # Scrna
  scrna_raw_props <- c(scrna_raw_props, obj@Tests$Scrna$Proportions$scrna_raw)
  scrna_pc_props <- c(scrna_pc_props, obj@Tests$Scrna$Proportions$scrna_pc)
  scrna_mdh_props <- c(scrna_mdh_props, obj@Tests$Scrna$Proportions$scrna_mdh)
  
  rm(obj)
  gc()
}

  
Seurat_props <- data.frame(overlap_seq, seurat_raw_props, seurat_pc_props, seurat_mdh_props)
colnames(Seurat_props) <- c("Overlap", "Baseline", "PCA", "MDH")

Seurat_melted <- data.table::melt(Seurat_props, id.vars = "Overlap", variable.name = "Reduction")

p1 <- ggplot2::ggplot(Seurat_melted) + geom_point(aes(Overlap, value, color = Reduction)) +
                                        xlab("Cluster Overlap") + ylab("Proportion") + theme_gray() +
                                            ggtitle("Seurat Significance Proportions") +
                                                  facet_grid(. ~ Reduction) 

Scrna_props <- data.frame(overlap_seq, scrna_raw_props, scrna_pc_props, scrna_mdh_props)
colnames(Scrna_props) <- c("Overlap", "Baseline", "PCA", "MDH")

Scrna_melted <- data.table::melt(Scrna_props, id.vars = "Overlap", variable.name = "Reduction")

p2 <- ggplot2::ggplot(Scrna_melted) + geom_point(aes(Overlap, value, color = Reduction)) +
                                        xlab("Cluster Overlap") + ylab("Proportion") + theme_gray() +
                                            ggtitle("Scrna Significance Proportions") +
                                                  facet_grid(. ~ Reduction) 
```


# save the plots
```{r}
pdf("/home/elijah/Documents/Clusterability/Results/Pipeline/Simulations/Cluster_Overlap_Proportions_Plots_1000.pdf", width = 10, height = 10)
t1 <- arrangeGrob(p1, p2, ncol = 2)
plot(t1)
dev.off()
```

# Simulate Paths
```{r}
paths <- seq(2, 52, 1)
# lists to hold test proportions
# Seurat
seurat_raw_props <- c()
seurat_pc_props <- c()
seurat_mdh_props <- c()

# Scrna
scrna_raw_props <- c()
scrna_pc_props <- c()
scrna_mdh_props <- c()


for(i in paths){
  
  cat(paste("\nRunning on",i,"Overlap\n"))
  
  params.groups <- newSplatParams(batchCells = 3000, nGenes = 2000, seed = 1994)
  
  # run simulations
  sim <- splatSimulatePaths(params.groups, path.length = i, de.prob = 0.5, de.facLoc = 0.5, verbose = FALSE)
  
  # sim_norm <- scater::normalize(sim)
  # p5 <- plotPCA(sim_norm, colour_by = "Step") + ggtitle(paste("PCA plot of path length 10"))
  # 
  
  # extract the counts
  sim_counts <- counts(sim)
  
  # run the pipeline
  obj <- CreateModalityObject(sim_counts)
  
  # add the seurat slot
  obj <- PreprocessObject(obj,  nFeatures = 1000)
  
  # add the scrna slot
  obj <- PreprocessObject(obj, method = "Scrna", nFeatures = 1000)
  
  # Run the Seurat modality tests
  obj <- TestModality(obj)
  obj <- TestModality(obj, type = "Scrna")
  
  
  # compute a result table for all the tests
  seurat <- as.data.frame(unlist(obj@Tests$Seurat))
  colnames(seurat) <- c("Seurat.Dip.Pvalue")
  
  scrna <- as.data.frame(unlist(obj@Tests$Scrna))
  colnames(scrna) <- c("Scrna.Dip.Pvalue")
  
  res_table <- cbind(scrna, seurat)
  
  # compute the proportions of passed test
  obj <- ComputeProportions(obj)
  
  # update the proportions
  # Seurat
  seurat_raw_props <- c(seurat_raw_props, obj@Tests$Seurat$Proportions$seurat_raw)
  seurat_pc_props <- c(seurat_pc_props, obj@Tests$Seurat$Proportions$seurat_pc)
  seurat_mdh_props <- c(seurat_mdh_props, obj@Tests$Seurat$Proportions$seurat_mdh)
  
  # Scrna
  scrna_raw_props <- c(scrna_raw_props, obj@Tests$Scrna$Proportions$scrna_raw)
  scrna_pc_props <- c(scrna_pc_props, obj@Tests$Scrna$Proportions$scrna_pc)
  scrna_mdh_props <- c(scrna_mdh_props, obj@Tests$Scrna$Proportions$scrna_mdh)
  
  rm(obj)
  gc()
}

  
Seurat_props <- data.frame(paths, seurat_raw_props, seurat_pc_props, seurat_mdh_props)
colnames(Seurat_props) <- c("NumPaths", "Baseline", "PCA", "MDH")

Seurat_melted <- data.table::melt(Seurat_props, id.vars = "NumPaths", variable.name = "Reduction")

p1 <- ggplot2::ggplot(Seurat_melted) + geom_point(aes(NumPaths, value, color = Reduction)) +
                                        xlab("Path Length") + ylab("Proportion") + theme_gray() +
                                            ggtitle("Seurat Significance Proportions") +
                                                  facet_grid(. ~ Reduction) 

Scrna_props <- data.frame(paths, scrna_raw_props, scrna_pc_props, scrna_mdh_props)
colnames(Scrna_props) <- c("NumPaths", "Baseline", "PCA", "MDH")

Scrna_melted <- data.table::melt(Scrna_props, id.vars = "NumPaths", variable.name = "Reduction")

p2 <- ggplot2::ggplot(Scrna_melted) + geom_point(aes(NumPaths, value, color = Reduction)) +
                                        xlab("Path Length") + ylab("Proportion") + theme_gray() +
                                            ggtitle("Scrna Significance Proportions") +
                                                  facet_grid(. ~ Reduction) 

```

## save the plots
```{r}
pdf("/home/elijah/Documents/Clusterability/Results/Pipeline/Simulations/Path_Lengths_Proportions_Plots_1000.pdf", width = 12, height = 8)
#t1 <- arrangeGrob(p3, p4, p5)
t2 <- arrangeGrob(p1, p2, ncol = 2)
#plot(t1)
plot(t2)
dev.off()
```
## write files to csv
```{r}
write.csv(Seurat_props, 
          file = "/home/elijah/Documents/Clusterability/Results/Pipeline/Simulations/Seurat_Path_Lengths_Proportions_Plots.csv")

write.csv(Scrna_props, 
          file = "/home/elijah/Documents/Clusterability/Results/Pipeline/Simulations/Scrna_Path_Lengths_Proportions_Plots.csv")
```


# Simulate a single cluster with increasing number of cells
```{r}
# lists to hold test proportions
# Seurat
seurat_raw_props <- c()
seurat_pc_props <- c()
seurat_mdh_props <- c()

# Scrna
scrna_raw_props <- c()
scrna_pc_props <- c()
scrna_mdh_props <- c()

# SC3
sc3_k <- c()

# simulation parameters
# prob_vec <- c(1/3, 1/3, 1/3)
cells_dim <- seq(1000, 12500, 500)

for(i in cells_dim){
  
  cat(paste("\nRunning on",i,"Cells\n"))
  
  params.groups <- newSplatParams(batchCells = i, nGenes = 2000, seed = 1994)
  
  # run simulations
  sim <- splatSimulateGroups(params.groups, verbose = FALSE)
  
  sim_norm <- scater::normalize(sim)
  p5 <- plotPCA(sim_norm) + ggtitle(paste("PCA plot of 13000 cells"))
  # plot(p)
  
  # extract the counts
  sim_counts <- counts(sim)
  
  # run the pipeline
  obj <- CreateModalityObject(sim_counts)
  
  # add the seurat slot
  obj <- PreprocessObject(obj,  nFeatures = 1000)
  
  # add the scrna slot
  obj <- PreprocessObject(obj, method = "Scrna", nFeatures = 1000)
  
  # Run the Seurat modality tests
  obj <- TestModality(obj)
  obj <- TestModality(obj, type = "Scrna")
  
  # compute a result table for all the tests
  seurat <- as.data.frame(unlist(obj@Tests$Seurat))
  colnames(seurat) <- c("Seurat.Dip.Pvalue")
  
  scrna <- as.data.frame(unlist(obj@Tests$Scrna))
  colnames(scrna) <- c("Scrna.Dip.Pvalue")
  
  res_table <- cbind(scrna, seurat)
  
  # compute the proportions of passed test
  obj <- ComputeProportions(obj)
  
  # update the proportions
  # Seurat
  seurat_raw_props <- c(seurat_raw_props, obj@Tests$Seurat$Proportions$seurat_raw)
  seurat_pc_props <- c(seurat_pc_props, obj@Tests$Seurat$Proportions$seurat_pc)
  seurat_mdh_props <- c(seurat_mdh_props, obj@Tests$Seurat$Proportions$seurat_mdh)
  
  # Scrna
  scrna_raw_props <- c(scrna_raw_props, obj@Tests$Scrna$Proportions$scrna_raw)
  scrna_pc_props <- c(scrna_pc_props, obj@Tests$Scrna$Proportions$scrna_pc)
  scrna_mdh_props <- c(scrna_mdh_props, obj@Tests$Scrna$Proportions$scrna_mdh)
  
  rm(obj)
  gc()
  
}

Seurat_props <- data.frame(cells_dim[1:24], seurat_raw_props, seurat_pc_props, seurat_mdh_props)
colnames(Seurat_props) <- c("nCells", "Baseline", "PCA", "MDH")

Seurat_melted <- data.table::melt(Seurat_props, id.vars = "nCells", variable.name = "Reduction")

p1 <- ggplot2::ggplot(Seurat_melted) + geom_point(aes(nCells/500, value, color = Reduction)) +
                                        xlab("Number of Cells * 500") + ylab("Proportion") + theme_gray() + 
                                        theme(plot.title = element_text(hjust = 0.5)) +
                                            ggtitle("Seurat Significance Proportions") +
                                                  facet_grid(. ~ Reduction) 

Scrna_props <- data.frame(cells_dim[1:24], scrna_raw_props, scrna_pc_props, scrna_mdh_props)
colnames(Scrna_props) <- c("nCells", "Baseline", "PCA", "MDH")

Scrna_melted <- data.table::melt(Scrna_props, id.vars = "nCells", variable.name = "Reduction")

p2 <- ggplot2::ggplot(Scrna_melted) + geom_point(aes(nCells/500, value, color = Reduction)) +
                                        xlab("Number of Cells * 500") + ylab("Proportion") + theme_gray() + 
                                          theme(plot.title = element_text(hjust = 0.5)) +
                                            ggtitle("Scrna Significance Proportions") +
                                                  facet_grid(. ~ Reduction) 
  
```

## save the plots
```{r}
pdf("/home/elijah/Documents/Clusterability/Results/Pipeline/Simulations/Cells_Proportions_Plots_1000.pdf", width = 12, height = 8)
#t1 <- arrangeGrob(p3, p4, p5)
t2 <- arrangeGrob(p1, p2, ncol = 2)
#plot(t1)
plot(t2)
dev.off()
```
## write files to csv
```{r}
write.csv(Seurat_props, 
          file = "/home/elijah/Documents/Clusterability/Results/Pipeline/Simulations/Seurat_Cells_Proportions_Plots.csv")

write.csv(Scrna_props, 
          file = "/home/elijah/Documents/Clusterability/Results/Pipeline/Simulations/Scrna_Cells_Proportions_Plots.csv")
```


# Simulation based on real data
```{r}
# get the counts
counts <- fread("Data/SPF_allTcells.txt") %>% column_to_rownames(var = "V1")

# get the parameters
params <- splatEstimate(as.matrix(counts))

# Run the easy simulation on four groups
sim <-  splatSimulate(params = params, batchCells = 3000,
                     group.prob = c(0.2, 0.15, 0.4, 0.25), 
                     method = "groups", de.prob = c(0.01, 0.05, 0.05, 0.08),
                     verbose = FALSE)

sim_norm <- scater::normalize(sim)
p3 <- plotPCA(sim_norm, colour_by = "Group")

sc3_sce <- sc3_estimate_k(sim_norm)
sc3_sce@metadata$sc3

# extract the counts
sim_counts <- counts(sim)

# run the pipeline
obj <- CreateModalityObject(sim_counts)

# add the seurat slot
obj <- PreprocessObject(obj,  nFeatures = 500)

# add the scrna slot
obj <- PreprocessObject(obj, method = "Scrna", nFeatures = 500)

# Run the Seurat modality tests
obj <- TestModality(obj)
obj <- TestModality(obj, type = "Scrna")


# compute a result table for all the tests
seurat <- as.data.frame(unlist(obj@Tests$Seurat))
colnames(seurat) <- c("Seurat.Dip.Pvalue")

scrna <- as.data.frame(unlist(obj@Tests$Scrna))
colnames(scrna) <- c("Scrna.Dip.Pvalue")

res.table <- cbind(scrna, seurat)

# plot heat map
obj.heatmap <- pheatmap(as.matrix(res.table), cluster_rows = F, cluster_cols = F, breaks = c(0, 0.05, 1), color = c("lightblue", "gray"), main = paste("Heatmap"))
heatmap <- as.ggplot(obj.heatmap)

seurat_pca_df <- as.data.frame(obj@Seurat$Sig.PCs.Data[, 1:2])
scrna_pca_df <- as.data.frame(obj@Scrna$Sig.PCs.Data[, 1:2])

# Run PCA
p.pca <- ggplot(seurat_pca_df) + geom_point(aes(PC_1, PC_2))  +
                                        xlab("PC1") + ylab("PC2") +  ggtitle(paste("Seurat PCA")) + theme_grey() +
                                          theme(plot.title = element_text(hjust = 0.5))
p.pca.scrna <- ggplot(scrna_pca_df) + geom_point(aes(PC1, PC2))  +
                                        xlab("PC1") + ylab("PC2") +  ggtitle(paste("Scrna PCA")) + theme_grey() +
                                          theme(plot.title = element_text(hjust = 0.5))

# Plot the Tsne
seurat.tsne <- as.data.frame(obj@Seurat$Tsne.Data)
p.seurat.tsne <-  ggplot(seurat.tsne) + geom_point(aes(V1, V2)) + labs(title = paste("Seurat Tsne"), x = "Tsne_1", y = "Tsne_2") + theme_gray() + theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90))

scrna.tsne <- as.data.frame(obj@Scrna$Tsne.Data)
p.scrna.tsne <-  ggplot(scrna.tsne) + geom_point(aes(V1, V2)) + labs(title = paste("Scrna Tsne"), x = "Tsne_1", y = "Tsne_2") + theme_gray() + theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90))

# plot UMAP
seurat.umap <- as.data.frame(obj@Seurat$Umap.Data)
p.seurat.umap <- ggplot(seurat.umap) + geom_point(aes(V1, V2)) + labs(title = paste("Seurat Umap"), x = "UMAP_1", y = "UMAP_1") + theme_gray() + theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90))

scrna.umap <- as.data.frame(obj@Scrna$Umap.Data)
p.scrna.umap <- ggplot(scrna.umap) + geom_point(aes(V1, V2)) + labs(title = paste("Scrna Umap"), x = "UMAP_1", y = "UMAP_1") + theme_gray() + theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90))

# plot Phate
seurat.phate <- as.data.frame(obj@Seurat$Phate.Data)
p.seurat.phate <-  ggplot(seurat.phate) + geom_point(aes(PHATE1, PHATE2)) + labs(title = paste("Seurat Phate"), x = "Phate_1", y = "Phate_2") + theme_gray() + theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90))

scrna.phate <- as.data.frame(obj@Scrna$Phate.Data)
p.scrna.phate <-  ggplot(scrna.phate) + geom_point(aes(PHATE1, PHATE2)) + labs(title = paste("Scrna Phate"), x = "Phate_1", y = "Phate_2") + theme_gray() + theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90))

# combine the plots
plots <- plot_grid(p.pca, p.pca.scrna, p.seurat.tsne, p.scrna.tsne, 
                       p.seurat.umap, p.scrna.umap, p.seurat.phate, p.scrna.phate, 
                   heatmap, labels = c("A", "B","C", "D", "E", "F","G", "H", "I"))
  
```

# create some data and shuffle it
```{r}
params.groups <- newSplatParams(batchCells = 2000, nGenes = 2000, seed = 1994)

# run simulations
sim <- splatSimulateGroups(params.groups, group.prob = c(0.4, 0.25, 0.35), de.facLoc = c(1,1,1)*0.1,
                               de.facScale = c(1,1,1)*0.1,  verbose = FALSE)

sim_norm <- scater::normalize(sim)
p3 <- plotPCA(sim_norm, colour_by = "Group") + ggtitle("Orginal PCA Plot") + theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90))

# sim.meta.data <- as.data.frame(sim@colData$Group)
# rownames(sim.meta.data) <- sim@colData$Cell
# colnames(sim.meta.data) <- c("Cluster")
# 
# sim.counts <- counts(sim)
# 
# obj <- CreateSeuratObject(sim.counts, meta.data = sim.meta.data, project = "Proj", min.cells = 5, min.features = 200)
# Idents(obj) <- "Cluster"
```


## Run on the first cluster
```{r}
# c1.counts <- as.matrix(GetAssayData(obj, slot = "counts")[, WhichCells(obj, idents = "Group1")])
# c2.counts <- as.matrix(GetAssayData(obj, slot = "counts")[, WhichCells(obj, idents = "Group2")])
sim.counts <- counts(sim)

# sim.counts <- sim.counts[, sample(4000, replace = T)]
# c1.counts <- sim.counts[, 1:2000]
# c2.counts <- sim.counts[, 2001:4000]
# # n <- nrow(c1.counts)
# c1.shuffled <- c1.counts[sample(ceiling(nrow(c1.counts))), ]
# c2.shuffled <- c2.counts[sample(nrow(c2.counts)), ]
# # 
# # c1.temp <- c1.counts[!rownames(c1.counts) %in% rownames(c1.shuffled), ]
# #c1.counts <- rbind(c1.temp, c1.shuffled)
# 
# c.all <- cbind(c1.counts, c2.counts)
true.clusters <- as.numeric(colData(sim)$Group)
# run the pipeline
obj <- CreateModalityObject(sim.counts)

# add the seurat slot
obj <- PreprocessObject(obj,  nFeatures = 500)

# add the scrna slot
obj <- PreprocessObject(obj, method = "Scrna", nFeatures = 500)


# sc3 analysis
sce <- SingleCellExperiment(
    assays = list(
        counts = as.matrix(obj@Seurat$Scaled.Data),
        logcounts = as.matrix(obj@Seurat$Scaled.Data)
    )
)
 
 sce <- sc3_estimate_k(sce)
 sce@metadata$sc3
 # define feature names in feature_symbol column
rowData(sce)$feature_symbol <- rownames(sce)
sce <- sc3(sce, ks = 3, biology = F, gene_filter = F)

# Run the Seurat modality tests
obj <- TestModality(obj)
obj <- TestModality(obj, type = "Scrna")


# compute a result table for all the tests
seurat <- as.data.frame(unlist(obj@Tests$Seurat))
colnames(seurat) <- c("Seurat.Dip.Pvalue")

scrna <- as.data.frame(unlist(obj@Tests$Scrna))
colnames(scrna) <- c("Scrna.Dip.Pvalue")

res.table <- cbind(scrna, seurat)
colnames(res.table) <- c("Seurat", "Scrna")

# plot heat map
obj.heatmap <- pheatmap(as.matrix(res.table), cluster_rows = F, cluster_cols = F, breaks = c(0, 0.05, 1), color = c("lightblue", "gray"), main = paste("Heatmap"))
heatmap <- as.ggplot(obj.heatmap)

seurat_pca_df <- as.data.frame(obj@Seurat$Sig.PCs.Data[, 1:2])
scrna_pca_df <- as.data.frame(obj@Scrna$Sig.PCs.Data[, 1:2])

# Run PCA
p.pca <- ggplot(seurat_pca_df) + geom_point(aes(PC_1, PC_2))  +
                                        xlab("PC1") + ylab("PC2") +  ggtitle(paste("Seurat PCA")) + theme_grey() +
                                          theme(plot.title = element_text(hjust = 0.5))
p.pca.scrna <- ggplot(scrna_pca_df) + geom_point(aes(PC1, PC2))  +
                                        xlab("PC1") + ylab("PC2") +  ggtitle(paste("Scrna PCA")) + theme_grey() +
                                          theme(plot.title = element_text(hjust = 0.5))

# Plot the Tsne
seurat.tsne <- as.data.frame(obj@Seurat$Tsne.Data)
p.seurat.tsne <-  ggplot(seurat.tsne) + geom_point(aes(V1, V2)) + labs(title = paste("Seurat Tsne"), x = "Tsne_1", y = "Tsne_2") + theme_gray() + theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90))

scrna.tsne <- as.data.frame(obj@Scrna$Tsne.Data)
p.scrna.tsne <-  ggplot(scrna.tsne) + geom_point(aes(V1, V2)) + labs(title = paste("Scrna Tsne"), x = "Tsne_1", y = "Tsne_2") + theme_gray() + theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90))

# plot UMAP
seurat.umap <- as.data.frame(obj@Seurat$Umap.Data)
p.seurat.umap <- ggplot(seurat.umap) + geom_point(aes(V1, V2)) + labs(title = paste("Seurat Umap"), x = "UMAP_1", y = "UMAP_1") + theme_gray() + theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90))

scrna.umap <- as.data.frame(obj@Scrna$Umap.Data)
p.scrna.umap <- ggplot(scrna.umap) + geom_point(aes(V1, V2)) + labs(title = paste("Scrna Umap"), x = "UMAP_1", y = "UMAP_1") + theme_gray() + theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90))

# # plot Phate
# seurat.phate <- as.data.frame(obj@Seurat$Phate.Data)
# p.seurat.phate <-  ggplot(seurat.phate) + geom_point(aes(PHATE1, PHATE2)) + labs(title = paste("Seurat Phate"), x = "Phate_1", y = "Phate_2") + theme_gray() + theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90))
# 
# scrna.phate <- as.data.frame(obj@Scrna$Phate.Data)
# p.scrna.phate <-  ggplot(scrna.phate) + geom_point(aes(PHATE1, PHATE2)) + labs(title = paste("Scrna Phate"), x = "Phate_1", y = "Phate_2") + theme_gray() + theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90))

# combine the plots
plots <- plot_grid(p3, p.pca, p.pca.scrna, p.seurat.tsne, p.scrna.tsne, 
                       p.seurat.umap, p.scrna.umap,
                   heatmap, labels = c("A", "B","C", "D", "E", "F","G", "H"))
```


# SC3 Analysis
```{r}
params.groups <- newSplatParams(batchCells = 3000, nGenes = 2000, seed = 1994)
sim <- splatSimulateGroups(params.groups, group.prob = c(0.5,0.5), de.facLoc = c(1, 1)*0.5,
                               de.facScale = c(1, 1)*0.5, verbose = FALSE, dropout.type = "experiment")

sim_norm <- scater::normalize(sim)
p3 <- plotPCA(sim_norm) + ggtitle("Orginal PCA Plot") + theme(plot.title = element_text(hjust = 0.5), axis.text.x = element_text(angle = 90))

counts <- counts(sim)
sce <- SingleCellExperiment(
    assays = list(
        counts = as.matrix(counts),
        logcounts = log2(as.matrix(counts) + 1)
    )
)

# define feature names in feature_symbol column
rowData(sce)$feature_symbol <- rownames(sce)
# remove features with duplicated names
sce <- sce[!duplicated(rowData(sce)$feature_symbol), ]
 
sce <- sc3(sce, ks = 2:3)

consensus <- metadata(sce)$sc3$consensus[[as.character(2)]]$consensus
```

# Consensus Clustering
```{r}
params.groups <- newSplatParams(batchCells = 5000, nGenes = 2000, seed = 1994)
sim <- splatSimulateGroups(params.groups, group.prob = c(1),
                               de.facScale = c(1))

sim.counts <- counts(sim)
obj <- CreateModalityObject(sim.counts)

obj <- PreprocessObject(obj,  nFeatures = 500)

# add the scrna slot
obj <- PreprocessObject(obj, method = "Scrna", nFeatures = 500)

seurat.con.res <- ConsensusClusterPlus(t(obj@Seurat$Scaled.Data), maxK=3,reps=100,pItem=0.8,pFeature=1,
                                       ,clusterAlg="hc",distance="pearson",seed=1994, verbose = T)[[3]][["consensusMatrix"]]
scrna.con.res <- ConsensusClusterPlus(t(obj@Scrna$Deviances), maxK=3,reps=100,pItem=0.8,pFeature=1,
                                       ,clusterAlg="hc",distance="pearson",seed=1994, verbose = T)[[3]][["consensusMatrix"]]
```

